Report

### 2020-11-13 report.Rmd
Improve plan

```{r}
temporal_dynamics_coef %>%
  filter(term %in% "slope", coeff %in% c("bm_std", "log_bm_std")) %>%
  select(1:4) %>%
  pivot_wider(names_from = "term", values_from = estimate) %>%
  left_join(biomass_group, by = c("station", "coeff" = "bm_var")) %>%
  filter(group_type == "median", summary_type %in% c("first_3_year", "median")) %>%
  ggplot(aes(x = bm, y = slope)) +
  geom_point(aes(color = group)) +
  facet_wrap(coeff~summary_type, scales = "free") +
  labs(x = "Summary of biomass (g)", y = "Slope (g.y^-1)")
```

@@

```{r}
loadd(log_bm_net_group_median)
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_wrap(~variable, scales = "free") +
  labs_log_bm_net_trends()
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_median %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_grid(variable~protocol_type, scales = "free") +
  labs_log_bm_net_trends()

log_bm_net_group_median %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
```

@@

```{r}
loadd(model_log_bm, summary_log_bm)
```

@@

unique(summary_log_bm$variable)
model_log_bm_table <- summary_log_bm %>%
  filter(model == "mod_bm_quad2") %>%
  filter(!variable %in% c("log_rich_std", "nbnode_std")) %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

model_log_bm_table[["reg_table"]] %>% 
  bind_rows(.) %>%
  mutate(variable = rep(model_log_bm_table[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    ) 
  )
```

```{r}
bind_rows(model_log_bm_table[["anova_table"]]) %>% 
  mutate(variable = rep(model_log_bm_table[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )

@@

```{r}
map_dfr(model_log_bm_table[["model_obj"]], broom::glance) %>%
  mutate(variable = model_log_bm_table[["variable"]]) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Model summary for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )
```

@@

```{r, fig.height = 12, fig.width = 12}
pred_log_bm_quad2 <- summary_log_bm %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

pred_log_bm_quad2_plot <- map2(model_log_bm$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
plot_grid(top, legend_quad2, rel_widths = c(1, .1))
```
-

@@

```{r}
loadd(habitat_press, habitat_pressure)
#habitat_press
```

```{r}
test <- log_bm_net_group_median %>%
  filter(variable == "connectance") %>%
  left_join(habitat_pressure, by = "station")
test %>%
  pivot_longer(
    cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
    names_to = "evt_var", values_to = "value") %>%
ggplot(aes(y = bm_slope, x = value)) +
geom_point() +
facet_wrap(~evt_var, scales = "free_x")
```

```{r}
loadd(region_polygon, station_analysis)

@@

```{r}
log_bm_net_group_median %>%
  filter(variable == "rich_std", bm_slope < 0) %>%
  left_join(habitat_pressure, by = "station") %>%
  pivot_longer(cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
    names_to = "evt_var", values_to = "value") %>%
ggplot(aes(y = linear_slope, x = value)) +
geom_point() +
facet_wrap(~evt_var, scales = "free_x")
```

```{r}
loadd(richness_group)
rich_std_f3y <- richness_group %>% 
  filter(rich_var == "rich_std", summary_type == "first_3_year", group_type ==
    "median") %>%
  select(station, rich)

log_bm_net_group_median %>%
  filter(variable == "rich_std", bm_slope < 0) %>%
  left_join(rich_std_f3y, by = "station") %>%
  ggplot(aes(y = linear_slope, x = rich)) +
  geom_point()
```

@@

p_rigal_decrease_increase_slope_st <- 
  st_decrease_increase_rigal_biomass %>%
  left_join(biomass_group, by = "station") %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = shape_class)) +
  geom_point() +
  facet_wrap(~variable)
p_rigal_decrease_increase_slope_st
```
### Tendancies in rigal increase / decrease

```{r}
loadd(bm_net_group_median, log_bm_net_group_median, bm_vs_net_trends)
bm_vs_net_trends %>%
  ggplot(aes(x = reg_weight)) +
  geom_histogram() +
  facet_wrap(~variable)

@@

log_bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Log Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
```

@@

```{r}
loadd(bm_net_group_median)
loadd(log_bm_net_group_median)

bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

@@

```{r}
pred_log_bm_quad <- summary_log_bm %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

test <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
  std_error = TRUE)
plot_grid(plotlist = test, labels = model_log_bm$variable)
```

```{r}
loadd(log_bm_net_group_median, vif_log_bm)

vif_log_bm %>%
  ggplot(aes(y= vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

@@

```{r}
loadd(model_log_bm_by_protocol, summary_log_bm_by_protocol)
```

```{r, eval = FALSE}
complete_log_quad2 <- summary_log_bm_by_protocol %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

@@

```{r, eval = FALSE}
filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["resume"]]
filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["anova"]]

filter(summary_log_bm_by_protocol, model == "mod_bm_quad")[["resume"]]
filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["anova"]]
```

@@

```{r}
pred_log_bm_quad2 <- summary_log_bm_by_protocol %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_by_protocol %<>% filter(protocol_type == "complete")

pred_log_bm_quad2_plot <- map2(model_log_bm_by_protocol$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
```

@@

```{r}
pred_log_bm_quad <- summary_log_bm_by_protocol %>%
  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_by_protocol %<>% filter(protocol_type == "complete")

pred_log_bm_quad_plot <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
  std_error = TRUE)
plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm$variable)
```

```{r, eval = FALSE}
pred <- summary_log_bm_by_protocol %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r, eval = FALSE}
pred <- summary_log_bm_by_protocol %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

>>>>

```{r}
temporal_dynamics_coef %>%
  filter(term %in% "slope", coeff %in% c("bm_std", "log_bm_std")) %>%
  select(station:estimate) %>%
  pivot_wider(names_from = "term", values_from = estimate) %>%
  left_join(biomass_group, by = c("station", "coeff" = "bm_var")) %>%
  filter(group_type == "median", summary_type %in% c("first_3_year", "median")) %>%
  ggplot(aes(x = bm, y = slope)) +
  geom_point(aes(color = group)) +
  facet_wrap(summary_type~coeff, scales = "free") +
  labs(x = "Summary of biomass (g)", y = "Slope (g.y^-1)")
```

@@

```{r, cache = FALSE}
loadd(log_bm_net_group_f3y, model_log_bm_f3y, summary_log_bm_f3y, vif_log_bm_f3y)
loadd(bm_net_group_median, bm_vs_net_trends)
loadd(habitat_press, habitat_pressure)
loadd(region_polygon, station_analysis)
loadd(richness_group)
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_f3y %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_wrap(~variable, scales = "free") +
  labs_log_bm_net_trends()
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_f3y %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_grid(variable~protocol_type, scales = "free") +
  labs_log_bm_net_trends()

log_bm_net_group_f3y %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
```

@@

@@

model_log_bm_f3y_table <- summary_log_bm_f3y %>%
  filter(model == "mod_bm_quad2") %>%
  filter(variable %in% get_com_str_var(all = FALSE)) %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

model_log_bm_f3y_table[["reg_table"]] %>% 
  bind_rows(.) %>%
  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )) %>% 
  kable_styling(latex_options =c("scale_down")) %>%
  #add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
  #column_spec(1:2, width = "3cm") %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
bind_rows(model_log_bm_f3y_table[["anova_table"]]) %>% 
  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )

@@

```{r}
map_dfr(model_log_bm_f3y_table[["model_obj"]], broom::glance) %>%
  mutate(variable = model_log_bm_f3y_table[["variable"]]) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Model summary for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )
```

@@

```{r, fig.height = 12, fig.width = 12}
pred_log_bm_quad2 <- summary_log_bm_f3y %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

pred_log_bm_quad2_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
plot_grid(top, legend_quad2, rel_widths = c(1, .1))
```
-

@@

```{r}
#habitat_press
```

```{r}
test <- log_bm_net_group_f3y %>%
  filter(variable == "connectance") %>%
  left_join(habitat_pressure, by = "station")
test %>%
  pivot_longer(
    cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
    names_to = "evt_var", values_to = "value") %>%
ggplot(aes(y = bm_slope, x = value)) +
geom_point() +
facet_wrap(~evt_var, scales = "free_x")
```

```{r}

@@

```{r}
log_bm_net_group_f3y %>%
  filter(variable == "rich_std", bm_slope < 0) %>%
  left_join(habitat_pressure, by = "station") %>%
  pivot_longer(cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
    names_to = "evt_var", values_to = "value") %>%
ggplot(aes(y = linear_slope, x = value)) +
geom_point() +
facet_wrap(~evt_var, scales = "free_x")
```

```{r}
rich_std_f3y <- richness_group %>% 
  filter(rich_var == "rich_std", summary_type == "first_3_year", group_type ==
    "median") %>%
  select(station, rich)

log_bm_net_group_f3y %>%
  filter(variable == "rich_std", bm_slope < 0) %>%
  left_join(rich_std_f3y, by = "station") %>%
  ggplot(aes(y = linear_slope, x = rich)) +
  geom_point()
```

@@

p_rigal_decrease_increase_slope_st <- 
  st_decrease_increase_rigal_biomass %>%
  left_join(biomass_group, by = "station") %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = shape_class)) +
  geom_point() +
  facet_wrap(~variable)
p_rigal_decrease_increase_slope_st
```

### Tendancies in rigal increase / decrease

```{r}
bm_vs_net_trends %>%
  ggplot(aes(x = reg_weight)) +
  geom_histogram() +
  facet_wrap(~variable)

@@

log_bm_net_group_f3y %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Log Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
```

@@

```{r}
bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

@@

```{r}
pred_log_bm_quad <- summary_log_bm_f3y %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

test <- map2(model_log_bm_f3y$data, pred_log_bm_quad$pred_df, plot_pred_data,
  std_error = TRUE)
plot_grid(plotlist = test, labels = model_log_bm_f3y$variable)
```

```{r}

vif_log_bm_f3y %>%
  ggplot(aes(y= vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

@@

```{r}
loadd(model_log_bm_f3y_by_protocol, summary_log_bm_f3y_by_protocol)
```

```{r, eval = FALSE}
complete_log_quad2 <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

@@

```{r, eval = FALSE}
filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["resume"]]
filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["anova"]]

filter(summary_log_bm_f3y_by_protocol, model == "mod_bm_quad")[["resume"]]
filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["anova"]]
```

@@

```{r}
pred_log_bm_quad2 <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_f3y_by_protocol %<>% filter(protocol_type == "complete")

pred_log_bm_quad2_plot <- map2(model_log_bm_f3y_by_protocol$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
```

@@

```{r}
pred_log_bm_quad <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_f3y_by_protocol %<>% filter(protocol_type == "complete")

pred_log_bm_quad_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad$pred_df, plot_pred_data,
  std_error = TRUE)
plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm_f3y$variable)
```

```{r, eval = FALSE}
pred <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r, eval = FALSE}
pred <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```
